---
title: "Citation Needed -- Analysis"
author: "Darren Abramson"
date: "July 23, 2015"
output: html_document
---

The data analysis for the facts and figures below consists of two stages:

1. Taking compressed complete dumps of the English wikipedia and processing them to extract citation needed tags
2. Analyzing the extracted tags in R.

The processing was done in Java with use of the WikiXMLJ package by Google. Information on the processing can be found in the [README] github.com/DarrenAbramson/CitationNeeded/).

This document was generated from a markdown file including all analysis, [Analysis.Rmd] (https://github.com/DarrenAbramson/CitationNeeded/blob/master/Analysis.Rmd).

```{r Process_2013_data, echo=FALSE, include=FALSE}
library(stringr)
library(zoo)

cnTable <- read.csv("2015.07.22 AD at 10:44:31 ADT.enwiki-20130805-pages-articles.xml.bz2.csv", header=TRUE, quote="", stringsAsFactors=FALSE)

cnTableWithDates <- cnTable[grep("date=", cnTable$tagContents), ]

getDateString <- function (x) 
{
  startIndex <- str_locate (x, "date=")[2] + 1
  endIndex <- str_locate(x, "\\}\\}") - 1
  dateInfo <- substr(x, startIndex, endIndex)
  dateInfo
}

myYearMon <- function (x)
{
  as.yearmon(x, "%B %Y")
}

trim.leading <- function (x)  sub("^\\s+", "", x)

# Get data just extracts the string of the tagContents beyond "date="

cnTableWithDates$dateString <- sapply(cnTableWithDates$tagContents, getDateString)

# Trims it down to the 20 next characters

cnTableWithDates$dateString <- strtrim(cnTableWithDates$dateString, 20)

# Trim initial white space

cnTableWithDates$dateString <- sapply(cnTableWithDates$dateString, trim.leading)

# Assume standard format now with initial string consisting of Month and Year

cnTableWithDates$YearMonDate <- sapply(cnTableWithDates$dateString, myYearMon)

# Age is difference in months from date of dump

cnTableWithDates$age <- (as.numeric(as.yearmon("Aug 2013")) - as.numeric(cnTableWithDates$YearMonDate)) * 12

# Remove rows with na age.

cnTableWithDatesClean <- cnTableWithDates[which(!is.na(cnTableWithDates$age)),]

# Remove malformed rows, i.e. age of tag > age of Wikipedia. or age of tag < 0

cnTableWithDatesClean <- cnTableWithDates[which(cnTableWithDates$age < 144 & cnTableWithDates$age >= 0),]

# NOTE: while crude, this results in over 95% of tags extracting successfully.
```

Histogram for 2013 data:
```{r Make_2013_histogram, echo=FALSE, include=FALSE}
hist(cnTableWithDatesClean$age)
```


```{r Process_2015_data, echo=FALSE, include=FALSE}
cnTable <- read.csv("2015.07.22 AD at 14:47:27 ADT.enwiki-20150602-pages-articles.xml.bz2.csv", header=TRUE, quote="", stringsAsFactors=FALSE)

cnTableWithDates <- cnTable[grep("date=", cnTable$tagContents), ]

trim.leading <- function (x)  sub("^\\s+", "", x)

# Get data just extracts the string of the tagContents beyond "date="

cnTableWithDates$dateString <- sapply(cnTableWithDates$tagContents, getDateString)

# Trims it down to the 20 next characters

cnTableWithDates$dateString <- strtrim(cnTableWithDates$dateString, 20)

# Trim initial white space

cnTableWithDates$dateString <- sapply(cnTableWithDates$dateString, trim.leading)

# Assume standard format now with initial string consisting of Month and Year

cnTableWithDates$YearMonDate <- sapply(cnTableWithDates$dateString, myYearMon)

# Age is difference in months from date of dump

cnTableWithDates$age <- (as.numeric(as.yearmon("Jun 2015")) - as.numeric(cnTableWithDates$YearMonDate)) * 12

# Remove rows with na age.

cnTableWithDatesClean <- cnTableWithDates[which(!is.na(cnTableWithDates$age)),]

# Remove malformed rows, i.e. age of tag > age of Wikipedia. or age of tag < 0

cnTableWithDatesClean <- cnTableWithDates[which(cnTableWithDates$age < 144 & cnTableWithDates$age >= 0),]

# NOTE: while crude, this results in over 95% of tagContents extracting successfully to year/month dates.
```

Histogram for 2015 data:
```{r Make_2015_Histogram, echo=FALSE, include=FALSE}
hist(cnTableWithDatesClean$age)
```

Other interesting information:
